Reasoning About a Machine with Local Capabilities

### 2019-02-01 toplas/paper.tex
Remove reference to missing figure
Update seL4 paragraph

The Appendix contains the implementation of all the macros used in
\texttt{scall}. The technical appendix~\citep{technical_appendix} contains more
detailed descriptions of all the macros as well as all implementations.
%\itoplassug{Suggestion: Add the call implementation (and possibly other macros?) in the above?}
We stress that the macros correspond to series of instructions as seen in
\figurename~\ref{fig:scall-impl} and \ref{fig:scall-rest-code}, and that they
are introduced for intelligibility. The examples of
\sectionname~\ref{sec:examples}, the program examples are stated using the
macros, but the proofs work on the expanded macros.
\end{toplas}

@@

\begin{toplas}
  \emph{Why use a logical relation and not a simpler proof technique?}
  The concept of a capability exists on different levels of the computer stack, so capabilities have been studied and safety properties proven about them in other contexts than assembly languages.
  Traditionally, logical relations have not been used for safety property proofs, so why do we need one here?
  To answer this question let's compare this work to \citet{sewel_integrity_2011} where they prove \textit{integrity} and \textit{authority confinement} for the seL4 Microkernel.
  % Describe what they prove
  The security properties they show are relative to a security policy that specifies the upperbound of capabilities a subject in the system can posses.
  The security policy is expressed as a collection of possible capabilities in the system, e.g.\ \textit{subject a can have a write capability for memory B.}
  However, they cannot express what \emph{subject a} will be able to store in \emph{memory B}.
  The worlds in our model can put restrictions on how a capability can be used by placing a protocol on part of the memory.
  This is exactly what allows us to prove the awkward example.
  We place a protocol on the memory where variable \texttt{x} is stored that says that it sometimes can be either $0$ or $1$, and at other times it has to be $1$.
  Capability safety is not just about the permission a capability carries, it is also about how the capability is used.
  Say for instance, a program has a write capability that will only be used to write even numbers.
  If this is the only write capability for that part of memory, then we should be able to rely on that part of memory only containing even numbers.
  In order to rely on this in our proofs, our notion of capability safety must be able to take the meaning of the program into account and express the memory invariant.
\end{toplas}
\itoplassug{Reviewer C, popl, would like to know how local capabilities relate to borrowing (see tex comment).}

>>>>

The Appendix contains the implementation of all the macros used in
\texttt{scall}. The technical appendix~\citep{technical_appendix} contains more
detailed descriptions of all the macros as well as all implementations.
%\itoplassug{Suggestion: Add the call implementation (and possibly other macros?) in the above?}
We stress that the macros correspond to series of instructions as seen in
\figurename~\ref{fig:scall-impl}, and that they
are introduced for intelligibility. The examples of
\sectionname~\ref{sec:examples}, the program examples are stated using the
macros, but the proofs work on the expanded macros.
\end{toplas}

@@

\begin{toplas}
  \emph{Why use a logical relation and not a simpler proof technique?}
  The concept of a capability exists on different levels of the computer stack, so capabilities have been studied and safety properties proven about them in other contexts than assembly languages.
  Traditionally, logical relations have not been used for safety property proofs, so why do we need one here?
  To answer this question let's compare this work to \citet{sewel_integrity_2011} where they prove \textit{integrity} and \textit{authority confinement} for the seL4 Microkernel.
  % Describe what they prove
  The security properties they show are relative to a security policy that specifies the upperbound of capabilities a subject in the system can posses.
  The security policy is expressed as a collection of possible capabilities in the system, e.g.\ \textit{subject a can have a write capability for memory B.}
  However, their policy are, in a sense, binary: either subject a can not write to memory B, or it can write anything.
  Our approach is much more fine-grained, allowing us to define, for example, a policy that subject a can write to memory B, but only if the value being written is an even number.
  Because our invariants are indexed by worlds themselves, we can even define a policy that capabilities written to memory B must respect certain other invariants themselves.
  It is exactly the expressive invariants that enable us to prove the awkward example.
  We place a protocol on the memory where variable \texttt{x} is stored that says that it sometimes can be either $0$ or $1$, and at other times it has to be $1$.

  Capability safety is not just about the permission a capability carries, it is also about how the capability is used.
  Say for instance, a program has a write capability that will only be used to write even numbers.
  If this is the only write capability for that part of memory, then we should be able to rely on that part of memory only containing even numbers.
  In order to rely on this in our proofs, our notion of capability safety must be able to take the meaning of the program into account and express the memory invariant.
\end{toplas}
\itoplassug{Reviewer C, popl, would like to know how local capabilities relate to borrowing (see tex comment).}
